A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-07-27 Manuscript/vaught_2017.tex
7/27/18_ver2

\begin{table}[]
\centering
\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
\begin{tabular}{llllll} \hline \hline
Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
J.26 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.51 \pm 0.80$ & $7.53 \pm 0.35 $\\
J.36 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.69 \pm 1.02$ & $5.83 \pm 0.49$\\
J.03 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.39 \pm 0.71$ & $12.7 \pm 1.71$\\
J.64 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.55 \pm 0.66$ & $13.2 \pm 0.26$\\
J.57 &  $-1.25 \pm 1.15   $ & 11& -$0.653 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
\end{tabular}
\end{table}

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.9]{../Figures/ew_comb.pdf}
\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies. The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}. We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galacy. There is significant scatter relative to the error bars at extended distances.}
\label{fig:ew_comb}
\end{figure*}

>>>>

\begin{table}[]
\centering
\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
\begin{tabular}{llllll} \hline \hline
Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
J.26 &  $-5.4 \pm 1.28 $ & 8 &     $\ \ \ 3.5 \pm 0.80$ & $7.5 \pm 0.35 $\\
J.36 &  $-5.6 \pm 0.12 $ & 15 & $\ \ \ 7.7 \pm 1.02$ & $5.8 \pm 0.49$\\
J.03 &  $-4.4 \pm 0.62 $ & 21 & $\ \ \ 5.4 \pm 0.71$ & $12.7 \pm 1.71$\\
J.64 &  $-18.2 \pm 0.13 $ & 10 & $\ \ \ 7.6 \pm 0.66$ & $13.2 \pm 0.26$\\
J.57 &  $-1.3 \pm 1.15   $ & 11& -$0.65 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
\end{tabular}
\end{table}

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.9]{../Figures/ew_comb.pdf}
\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies. The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}. We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy. There is significant scatter relative to the error bars at extended distances.}
\label{fig:ew_comb}
\end{figure*}
